Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
conclusions

We found, in particular, that within the interpretation these theories as EFTs and the
region of validity of the ParSpec framework, the coupling constant of dCS gravity is bound to
$\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
of GW150914 and GW200129.
%
In contrast, we could not place any constraint of the coupling constants in
EdGB gravity $\ell_{\rm EdGB}$.
%
This dichotomy between the two theories has an analogy with works that considered
the inspiral part of the GW signal alone.
%
In that case, it is dCS gravity which cannot be constrained with current GW
events, while EdGB can, as shown in Refs.~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
This result also shows how the inclusion of theory-specific information into the ParSpec framework
can result in different outcomes for different theories, even if they predict same exponent $p$.

>>>>

We found, that within the interpretation these theories as EFTs and the
region of validity of the ParSpec framework, that the coupling constant of dCS gravity is bound as
$\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
of GW150914 and GW200129. This is the first GW-alone constrain on this theory.
%
In contrast, we could not place any bounds on the coupling constant of EdGB
gravity $\ell_{\rm EdGB}$.

This dichotomy between the two theories has a counterpart with works that considered
the inspiral part of the GW signal alone~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
In those cases, it is dCS gravity which cannot be constrained with current GW
events, while EdGB can.
%
We emphasize that both theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
%
Hence, our results show how the inclusion of theory-specific information into the ParSpec framework
can result in different outcomes for different theories, even if they predict same value of $p$.
